GNSS-based Displacement Detection Using Bayesian Inference for Deformation Monitoring

### 2021-03-22 paper/manuscript-cmame.tex

		\author[a]{Nan Shen}
		\author[a]{Liang Chen\corref{mycorrespondingauthor}}
		\cortext[mycorrespondingauthor]{Corresponding author}
		\ead{l.chen@whu.edu.cn}
		\author[a]{Ruizhi Chen}
		\address[a]{State Key Laboratory of Information Engineering in Surveying, Mapping and Remote Sensing, Wuhan University, Wuhan 430000, PR China}
		\begin{abstract}
		For decades, displacement detection based on the Global navigation satellite system (GNSS) has increasingly been important for a wide range of applications, from landslide monitoring, subsidence survey, to industrial measurement. 
		Most of the GNSS-based displacement detection methods in these applications are based on GNSS long-term static positioning results.
		With the development of Internet of Things (IoT), high-precision GNSS positioning, and GNSS related transmission protocol, kinematic positioning results can be transmitted to the cloud in real-time.
		However, due to the influence of measurement noise, it is still a challenge to identify and extract displacement from GNSS kinematic positioning results in a short time.
		To resolve this, we propose a novel displacement detection approach with the purpose of identifying and extracting displacement from GNSS kinematic positioning.
		Specifically, we use the Bayesian inference model to obtain the displacement change time from the coordinate time series of GNSS kinematic positioning. 
		%The likelihood function of the observation and the prior distribution of the parameters to be estimated are provided.
		%Finally, Bayesian inference was implemented by Markov Chain Monte Carlo (MCMC) sampling.
		By investigating the posterior distribution of the designed change point parameter, we can identify the change points.
		Furthermore, we derive the mean value from the posterior distribution of the mean parameter, and further obtain the displacement.
		Results from simulation and field experiments have demonstrated the effectiveness and flexibility of the proposed method.
		For significant displacement, it can be clearly identified; for small displacement, it can be identified by adding an interval constraint prior. The accuracy of up-displacement extraction from GNSS real-time kinematic positioning can reach within 2 mm in 15 minutes.		
		\end{abstract}

>>>>

		\author[a]{Nan Shen}
		\author[a]{Liang Chen\corref{mycorrespondingauthor}}
		\cortext[mycorrespondingauthor]{Corresponding author}
		\ead{l.chen@whu.edu.cn}
		\author[a]{Ruizhi Chen}
		\address[a]{State Key Laboratory of Information Engineering in Surveying, Mapping and Remote Sensing, Wuhan University, Wuhan 430000, PR China}
		\begin{abstract}
		For decades, displacement detection based on the Global navigation satellite system (GNSS) has increasingly been important for a wide range of applications, from landslide monitoring, subsidence survey, to industrial measurement. 
		Most of the GNSS-based displacement detection methods in these applications are based on GNSS long-term static positioning results.
		With the development of the Internet of Things (IoT), high-precision GNSS positioning, and GNSS-related transmission protocol, kinematic positioning results can be transmitted to the cloud in real-time.
		However, due to the influence of measurement noise, it is still a challenge to identify and extract displacement from GNSS kinematic positioning results in a short time.
		To resolve this, we propose a novel displacement detection approach with the purpose of identifying and extracting displacement from GNSS kinematic positioning.
		Specifically, we use the Bayesian inference model to obtain the displacement change time from the coordinate time series of GNSS kinematic positioning. 
		%The likelihood function of the observation and the prior distribution of the parameters to be estimated are provided.
		%Finally, Bayesian inference was implemented by Markov Chain Monte Carlo (MCMC) sampling.
		By investigating the posterior distribution of the designed change point parameter, we can identify the change points.
		Furthermore, we derive the mean value from the posterior distribution of the mean parameter, and further obtain the displacement.
		Results from simulation and field experiments have demonstrated the effectiveness and flexibility of the proposed method.
		For significant displacement, it can be clearly identified; for small displacement, it can be identified by adding an interval constraint prior. The accuracy of up-displacement extraction from GNSS real-time kinematic positioning can reach within 2 mm in 15 minutes.		
		\end{abstract}
